Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-09-07 main.tex
Put the elements into place
Update abstract
Update keywords

% Start the abstract
\begin{abstract}
\ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used to the design of new \ac{cad} systems.
\ac{dce}-\ac{mri} is one of the modality regularly used in \ac{mpmri} \ac{cad} system.
Pharmocokinetric parameters are extracted from the \ac{dce}-\ac{mri} sequences and later used to discriminate cancerous from healthy tissue.
However, some inter-patients variations occur during the data acquisition leading to estimation errors of the pharmacokinetic parameters.
Therefore, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
The benefit and simplicity of our approach is shown by detecting cancerous voxel from healthy voxel using the normalized enhanced \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
Additionally, we show that using this normalization approach in conjunction with the quantitative methods improves the classification performance of most of the models.
The best classification performance to detect \ac{cap} is obtained using the whole \ac{dce}-\ac{mri} normalized signal, reaching an \ac{auc} of $0.666\ (\pm 0.154)$ and outperforming the quantitative approaches.
\end{abstract}

% Give the different keywords
\begin{keyword}
\acs*{dce}-\acs*{mri}\sep prostate cancer\sep normalization\sep classification\sep quantification
\end{keyword}

>>>>

% Start the abstract
\begin{abstract}
\Ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used to the design of new \ac{cad} systems.
\ac{dce}-\ac{mri} is one of the modality regularly used in \ac{mpmri} \ac{cad} system.
Pharmocokinetric parameters are extracted from the \ac{dce}-\ac{mri} sequences and later used to discriminate cancerous from healthy tissue.
However, some inter-patients variations occur during the data acquisition leading to estimation errors of the pharmacokinetic parameters.
Therefore, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
The benefit and simplicity of our approach is shown by detecting cancerous voxel from healthy voxel using the normalized enhanced \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
Additionally, we show that using this normalization approach in conjunction with the quantitative methods improves the classification performance of most of the models.
The best classification performance to detect \ac{cap} is obtained using the whole \ac{dce}-\ac{mri} normalized signal, reaching an \ac{auc} of $0.666\ (\pm 0.154)$ and outperforming the quantitative approaches.
\end{abstract}

% Give the different keywords
\begin{keyword}
\acs*{dce}-\acs*{mri}\sep prostate cancer\sep normalization\sep classification
\end{keyword}
